material and methods

### 2017-11-13 man/ms_1_material_methods.Rmd
update

To explore the effect of drought events on greenness we calculated the EVI standardized anomaly (EVI~sa) pixel-by-pixel, since it minimizes biases in the evaluation of anomalies, providing more information about the magnitude of the anomalies [@Samanta2012, @Gao2016]. For each pixel we averaged all the EVI valid values within a year (:red_filter: see quality filter), and then the standardized anomaly was computed as:

>>>>

To explore the effect of drought events on greenness we calculated the EVI standardized anomaly ($EVI~sa$) pixel-by-pixel, since it minimizes biases in the evaluation of anomalies, providing more information about the magnitude of the anomalies [@Samanta2012, @Gao2016]. For each pixel we averaged all the EVI valid values within a year (:red_filter: see quality filter), and then the standardized anomaly was computed as:
